### 2012-06-19 inst/examples/value_of_information.Rmd
debug growth on value_of_information

``` {r simfn} 
simulatereps <- function(opt, true_g, true_m, true_i){
  z_g <- function() rlnorm(1,  0, true_g) 
  z_m <- function() rlnorm(1,  0, true_m) 
  z_i <- function() rlnorm(1,  0, true_i)

@@

``` {r runallsims} 
policyfn <- list(det=det, g=g, m=m, i=i, gm=gm, gi=gi, gmi=gmi)
noise <- list(s0=c(0,0,0), sg=c(.2, 0, 0), sm=c(0, .2, 0), si=c(0,0,.2), sgm=c(.2, .2, 0), sgi=c(.2, 0, .2), sgmi=c(.2, .2, .2)) 
allcases <- lapply(policyfn, function(policyfn_i){
  lapply(noise, function(noise_i){
    simulatereps(policyfn_i, noise_i[1], noise_i[2], noise_i[3])
  })
})
````

``` {r tidyall}
sims <- unlist(allcases, recursive=FALSE)
dat <- melt(sims, id=names(sims[[1]][[1]]))  
dt <- data.table(dat)
setnames(dt, c("L2", "L1"), c("reps", "uncertainty")) # names are nice
````

>>>>

**quick debug check -- make z_g shocks only negative to confirm growth noise isn't good**

``` {r simfn} 
simulatereps <- function(opt, true_g, true_m, true_i){
  z_g <- function() min(rlnorm(1,  0, true_g), 1)
  z_m <- function() rlnorm(1,  0, true_m) 
  z_i <- function() rlnorm(1,  0, true_i)

@@

``` {r runallsims, dependson="simfn"} 
policyfn <- list(det=det, g=g, m=m, i=i, gm=gm, gi=gi, gmi=gmi)
noise <- list(s0=c(0,0,0), sg=c(.2, 0, 0), sm=c(0, .2, 0), si=c(0,0,.2), sgm=c(.2, .2, 0), sgi=c(.2, 0, .2), sgmi=c(.2, .2, .2)) 
allcases <- lapply(policyfn, function(policyfn_i){
  lapply(noise, function(noise_i){
    simulatereps(policyfn_i, noise_i[1], noise_i[2], noise_i[3])
  })
})
````

``` {r tidyall, dependson="runallsims"}
sims <- unlist(allcases, recursive=FALSE)
dat <- melt(sims, id=names(sims[[1]][[1]]))  
dt <- data.table(dat)
setnames(dt, c("L2", "L1"), c("reps", "uncertainty")) # names are nice
````
